Induced universal graphs for families of small graphs

### 2021-08-27 paper/paper.tex
Add better heuristic solver, and finish first draft of paper

\title{Small induced universal graphs}
\author{
        James Trimble \\
                School of Computing Science\\
        University of Glasgow, Glasgow, Scotland \\
}
\date{\today}

@@

\maketitle
%
\begin{abstract}
Using the results of brute-force computational experiments, we give for $0 \leq
k \leq 5$ the minimum number of vertices $f(k)$ in a graph containing all
$k$-vertex graphs as induced subgraphs.  We give the corresponding results for
$0 \leq k \leq 6$ for graphs containing all trees on $k$ vertices.  We also show
that $13 \leq f(6) \leq 15$.
\end{abstract}

@@

Given a collection $\calF$ of graphs, graph $G$ is \emph{induced
universal} for $\calF$ if and only if each element of $\calF$ is an induced
subgraph of $G$.  Graph $G$ is a \emph{minimal} induced universal graph
for $\calF$ if it has as few vertices as possible.  We write $f(k)$ to denote
    the order (number of vertices) of a minimal induced universal graph for the
    family of all graphs on $k$ vertices.  Moon showed that $f(k) \leq 2^{(k-1)/2}$
    \cite{moon_1965}, and Alon showed that $f(k) = (1 + o(1))2^{(k-1)/2}$
    \cite{alon2017asymptotically}.  There is an extensive literature on bounds
    on the order of minimal induced universal subgraphs for many families of
    graphs; see the references in \cite{alon2017asymptotically}.  However, I am
    not aware of any existing systematic attempts to find exact values for
    families of small graphs.  This paper presents exact values of $f(k)$ for
    $k \leq 5$, obtained by brute-force computational search.  The
    corresponding counts of minimal induced universal subgraphs, and results for
    families of trees, are also
    presented.

\section{Method}

Given values of $k$ and $n$,
a simple brute-force approach was used to find the set of
$n$-vertex graphs that are induced universal for the family $\calF$ of all $k$-vertex
graphs.  Each possible $n$-vertex graph $G$ from Brendan McKay's lists of
graphs\footnote{\url{https://users.cecs.anu.edu.au/~bdm/data/graphs.html}} was
tested in turn.  We used a Python implementation of the McSplit
algorithm \cite{DBLP:conf/ijcai/McCreeshPT17} to test whether each $k$-vertex
graph is an induced subgraph of $G$.  Although the McSplit algorithm was designed for
the more general maximum common induced subgraph problem, it performs well on
the subgraph isomorphism problem if both input graphs are small.

For those graphs $G$ that do not contain a copy of each element of $\calF$, it
is desirable to iterate over $\calF$ in an order that allows us to quickly
reject $G$ by finding a graph that is not an induced subgraph of $G$.  The approach we
used was to sort $\calF$ in descending order of number of isomorphisms.  In
particular, this means that the clique $K_k$ and the independent set $I_k$ are
the first two graphs tested.

The full set of experiments described in this paper, run sequentially, required
around 14 million calls to the subgraph isomorphism algorithm and took around
12 minutes to complete on a laptop.  \footnote{The code and results from this
paper, including lists of minimal induced universal graphs graph6 format, are
available from \url{https://github.com/jamestrimble/small-universal-graphs}}.

\section{Results}

Table~\ref{tab:graphresults} shows, for $0 \leq k \leq 5$, the value of $f(k)$.
The table also shows $F(k)$, the number of minimal induced universal
graphs for the family of all $k$-vertex graphs.  To my knowledge, the value of
$f(10)$ and the values of $F(k)$ have not been published previously.

The values $f(1)$, $f(2)$ and $f(3)$ are equal to to the simple lower bound $2k
- 1$ given in a question by ``Chain Markov'' on Mathematics Stack Exchange
\cite{math_se_question}.  The values $f(4)$ and $f(5)$ are equal to a lower
bound given in a comment by ``bof'' on that question: $f(k) \geq 2k$ if $k \geq
4$.  (For $k < 10$, this bound improves upon Moon's lower bound.)  To briefly
summarise the proof, if $k \leq 2k$ then $G$ must be a split graph (that is, a
graph whose vertices can be partitioned into a clique and an independent set);
therefore, $G$ cannot contain the cycle $C_4$ as an induced subgraph.  An
example of an 8-vertex induced universal graph for the family of 4-vertex
graphs was given by ``Chain Markov'' as a comment on the same question.

@@

\begin{figure}[h]
    \centering

@@

\section{Bounds on $f(6)$}

For $k > 6$, we can increase by 2 the lower bound by ``bof'' from the previous
section.

\begin{proposition}\label{f6proposition}
    $f(k) \geq 2k + 2$ for all $k > 5$.
\end{proposition}
\begin{proof}

    Suppose that $G$ is an induced universal graph
    for the family of all graphs on $k$ vertices, and that $G$ has no
    more than $2k + 1$ vertices.  Graph $G$ must have
    $K_k$ and $I_k$ as induced sugraphs.  This clique and independent set may
    overlap by no more than one vertex.
    Therefore it is possible to partition the vertices of $G$ into
    three sets: a clique $S_1$,
    an independent set $S_2$, and a set $S_3$
    containing at most 2 vertices.

    We will show that that $G$ can contain as an induced subgraph at most
    one of the complementary graphs in Figure~\ref{fig:boundproof}, which we
    call $H$ and $H'$ respectively.
    First, let $G_1$ be an induced
    subgraph of $G$ that is isomorphic to $H$.  Since there are
    no edges between the two three-vertex cliques in $G_1$, it must be the case that the
    vertex set of at least one of these cliques does not intersect $S_1$.
    Since $S_2$ is an independent set in $G$, this clique must have exactly
    one vertex in $S_2$ and two vertices in $S_3$.  We can deduce, then, that
    $S_3$ contains exactly two vertices, and that these vertices are adjacent in $G$.

\begin{figure}[h]
    \centering

@@

    Now consider graph $H'$.  Since $H'$ is an induced subgraph of $G$, it
    follows by taking complements of $H'$ and $G$ that $H$ is an induced
    subgraph of $G'$ (the complement of $G$).  We can repeat the argument
    of the previous paragraph with the roles of $S_1$ and $S_2$ reversed to
    show that the two vertices in $S_3$ must be adjacent in the complement of
    $G$, and therefore not adjacent in $G$.  Since we previously showed that
    these vertices are adjacent in $G$, we have a contradiction.
\end{proof}

To give a lower bound of 14 on $f(6)$, Figure~\ref{fig:adjmat14} shows the
adjacency matrix of a 14-vertex graph that is induced universal for the family
of all graphs on six vertices.  This was generated using a specialised random
graph generator.  We number the vertices from zero; the generator makes the
$k$ vertices numbered $0$ to $k-1$ a clique, and the $k$ vertices numbered $k-1$ to $2k-2$ an
independent set.  Each possible edge that is not involved in either the clique
or the independent set is added with probability $1/2$.  It was only necessary
to generate 53 graphs with this generator to find a solution TODO fixme.

TODO: give more details of generator

\begin{figure}[h]
\centering
\small
\verb|0 1 1 1 1 1 0 1 1 0 0 0 1 0| \\
\verb|1 0 1 1 1 1 1 1 1 1 1 0 0 1| \\
\verb|1 1 0 1 1 1 0 1 1 0 1 0 1 0| \\
\verb|1 1 1 0 1 1 1 0 0 0 1 1 0 0| \\
\verb|1 1 1 1 0 1 0 1 0 0 0 0 0 0| \\
\verb|1 1 1 1 1 0 0 0 0 0 0 1 0 1| \\
\verb|0 1 0 1 0 0 0 0 0 0 0 1 1 1| \\
\verb|1 1 1 0 1 0 0 0 0 0 0 1 1 0| \\
\verb|1 1 1 0 0 0 0 0 0 0 0 0 1 0| \\
\verb|0 1 0 0 0 0 0 0 0 0 0 1 0 1| \\
\verb|0 1 1 1 0 0 0 0 0 0 0 1 1 0| \\
\verb|0 0 0 1 0 1 1 1 0 1 1 0 0 1| \\
\verb|1 0 1 0 0 0 1 1 1 0 1 0 0 0| \\
\verb|0 1 0 0 0 1 1 0 0 1 0 1 0 0|
\caption{The adjacency matrix of a 14-vertex induced universal graph for the family of all
six-vertex graphs}
\label{fig:adjmat14}
\end{figure}

Thus, we have that $f(6) = 14$.

\section{Trees}

@@

\begin{figure}[h]
    \centering
\begin{tikzpicture}[>=latex',line join=bevel,scale=.4]
  \pgfsetlinewidth{.5bp}
%%
\pgfsetcolor{black}
  % Edge: 6 -- 0
  \draw [] (33.468bp,122.33bp) .. controls (44.467bp,128.89bp) and (59.197bp,137.66bp)  .. (70.288bp,144.27bp);
  % Edge: 6 -- 1
  \draw [] (30.834bp,100.1bp) .. controls (39.774bp,91.035bp) and (51.646bp,78.993bp)  .. (60.571bp,69.941bp);
  % Edge: 7 -- 0
  \draw [] (108.35bp,211.0bp) .. controls (103.69bp,198.96bp) and (97.434bp,182.81bp)  .. (92.754bp,170.73bp);
  % Edge: 7 -- 2
  \draw [] (128.78bp,216.26bp) .. controls (138.81bp,207.93bp) and (152.29bp,196.74bp)  .. (162.31bp,188.42bp);
  % Edge: 7 -- 3
  \draw [] (111.85bp,245.92bp) .. controls (109.9bp,257.68bp) and (107.35bp,272.94bp)  .. (105.4bp,284.67bp);
  % Edge: 8 -- 0
  \draw [] (134.88bp,109.4bp) .. controls (124.44bp,118.9bp) and (110.07bp,131.98bp)  .. (99.64bp,141.47bp);
  % Edge: 8 -- 1
  \draw [] (132.46bp,88.608bp) .. controls (119.73bp,81.799bp) and (101.96bp,72.297bp)  .. (89.227bp,65.491bp);
  % Edge: 8 -- 2
  \draw [] (154.41bp,114.43bp) .. controls (159.1bp,127.91bp) and (165.58bp,146.51bp)  .. (170.24bp,159.91bp);
  % Edge: 8 -- 4
  \draw [] (166.38bp,93.965bp) .. controls (179.82bp,91.611bp) and (198.11bp,88.409bp)  .. (211.53bp,86.058bp);
  % Edge: 8 -- 5
  \draw [] (152.57bp,79.558bp) .. controls (155.7bp,66.447bp) and (159.96bp,48.609bp)  .. (163.09bp,35.509bp);
  % Node: 0
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (86.17bp,153.73bp) ellipse (18.0bp and 18.0bp);
\end{scope}
  % Node: 1
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (73.34bp,56.99bp) ellipse (18.0bp and 18.0bp);
\end{scope}
  % Node: 2
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (176.16bp,176.91bp) ellipse (18.0bp and 18.0bp);
\end{scope}
  % Node: 3
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (102.42bp,302.6bp) ellipse (18.0bp and 18.0bp);
\end{scope}
  % Node: 4
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (229.48bp,82.92bp) ellipse (18.0bp and 18.0bp);
\end{scope}
  % Node: 5
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (167.27bp,18.0bp) ellipse (18.0bp and 18.0bp);
\end{scope}
  % Node: 6
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (18.0bp,113.12bp) ellipse (18.0bp and 18.0bp);
\end{scope}
  % Node: 7
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (114.87bp,227.81bp) ellipse (18.0bp and 18.0bp);
\end{scope}
  % Node: 8
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (148.38bp,97.12bp) ellipse (18.0bp and 18.0bp);
\end{scope}
%
\end{tikzpicture}

>>>>

\title{Induced universal graphs for families of small graphs}
\author{
        James Trimble \\
                School of Computing Science\\
        University of Glasgow, Glasgow, Scotland \\
}
\date{\today}

@@

\maketitle
%
\begin{abstract}
For $0 \leq
k \leq 6$, we give the minimum number of vertices $f(k)$ in a graph containing all
$k$-vertex graphs as induced subgraphs, and show
that $16 \leq f(7) \leq 18$.  For $0 \leq k \leq 5$, we also give the counts of
such graphs, as generated by brute-force computer search.  We give additional
results for small graphs containing all trees on $k$ vertices.
\end{abstract}

@@

Given a collection $\calF$ of graphs, graph $G$ is \emph{induced universal} for
$\calF$ if and only if each element of $\calF$ is an induced subgraph of $G$.
Graph $G$ is a \emph{minimal} induced universal graph for $\calF$ if it has as
few vertices as possible.  We write $f(k)$ to denote the order (that is, the
number of vertices) of a minimal induced universal graph for the family of all
graphs on $k$ vertices.  Moon showed that $f(k) \leq 2^{(k-1)/2}$
\cite{moon_1965}, and Alon showed that $f(k) = (1 + o(1))2^{(k-1)/2}$
\cite{alon2017asymptotically}.  There is an extensive literature on bounds on
the order of minimal induced universal subgraphs for many families of graphs;
see the references in \cite{alon2017asymptotically}.  However, I am not aware
of any existing systematic attempts to find exact values for families of small
graphs.  This paper presents exact values of $f(k)$ for $k \leq 6$ and bounds
on $f(7)$; in each case, the upper bounds were determined by brute-force
computational search and proofs are given for the lower bounds.  The
corresponding counts of minimal induced universal subgraphs for $0 \leq k \leq
5$, and results for families of trees, are also presented.

\section{Method for generating all induced universal graphs}

Given $k$ and $n$,
a simple brute-force approach was used to find the set of
$n$-vertex graphs that are induced universal for the family $\calF(k)$ of all $k$-vertex
graphs.  Each possible $n$-vertex graph $G$ from Brendan McKay's lists of
graphs\footnote{\url{https://users.cecs.anu.edu.au/~bdm/data/graphs.html}} was
tested in turn.  We used a Python implementation of the McSplit
algorithm \cite{DBLP:conf/ijcai/McCreeshPT17} to test whether each $k$-vertex
graph is an induced subgraph of $G$.  Although the McSplit algorithm was designed for
the more general maximum common induced subgraph problem, it performs well on
the subgraph isomorphism problem if both input graphs are small.  (Although
we have described the application of this method to families of all graphs of a given order,
our method could easily be applied to any family $\calF$ of graphs, and indeed
Section~\ref{sec:trees} gives results from the application of this method
to families of trees.)

For those graphs $G$ that do not contain a copy of each element of $\calF(k)$,
it improves the speed of our algorithm if we can iterate over
$\calF(k)$ in an order that allows us to quickly reject $G$ by finding a graph
that is not an induced subgraph of $G$.  The approach we used was to sort
$\calF(k)$ in descending order of number of isomorphisms.  In particular, this
means that the clique $K_k$ and the independent set $I_k$ are the first two
graphs tested.

The full set of experiments described in this paper, run sequentially, required
took less than an hour complete on a laptop with an Intel Core i5-6200U CPU
and 8 GB RAM.\footnote{The code and
results from this paper, including lists of minimal induced universal graphs
in graph6 format, are available from
\url{https://github.com/jamestrimble/small-universal-graphs}}

\section{Results for $k \leq 5$}

Table~\ref{tab:graphresults} shows, for $0 \leq k \leq 5$, the value of $f(k)$.
The table also shows $F(k)$, the number of minimal induced universal
graphs for the family of all $k$-vertex graphs.  To my knowledge, the value of
$f(5)$ and the values of $F(k)$ have not been published previously.

The values $f(1)$, $f(2)$ and $f(3)$ are equal to to the simple lower bound $2k
- 1$ given in a question by ``Chain Markov'' on Mathematics Stack Exchange
  \cite{math_se_question}.  The values $f(4)$ and $f(5)$ are equal to a lower
  bound given in a comment by ``bof'' on the same question: $f(k) \geq 2k$ if $k
  \geq 4$.  (For $k < 10$, this bound improves upon Moon's lower bound $f(k)
  \leq 2^{(k-1)/2}$.) To briefly summarise the proof, if $k \leq 2k$ then $G$
  must be a split graph (that is, a graph whose vertices can be partitioned
  into a clique and an independent set); therefore, $G$ cannot contain the
  cycle $C_4$ as an induced subgraph.  An example of an 8-vertex induced
  universal graph for the family of 4-vertex graphs was given by ``Chain
  Markov'' as a comment on the same question.

@@

\begin{figure}[htb]
    \centering

@@

\section{$f(6) = 14$}\label{sec:f6}

This section shows that $f(6) = 14$.  We begin with the lower bound.
For $k \geq 6$, we can increase by 2 the lower bound by ``bof''.  In particular,
this means that $f(6) \geq 14$.

\begin{proposition}\label{f6proposition}
    $f(k) \geq 2k + 2$ for all $k \geq 6$.
\end{proposition}
\begin{proof}

    Suppose that $G$ is an induced universal graph for the family of all graphs
    on $k$ vertices, and that $G$ has no more than $2k + 1$ vertices.  Graph
    $G$ must have $K_k$ and $I_k$ as induced sugraphs.  This clique and
    independent set may overlap by no more than one vertex, so their union must
    contain at least $2k - 1$ vertices.  Therefore it is possible to partition
    the vertices of $G$ into three sets: a clique $S_1$, an independent set
    $S_2$, and a third set $S_3$ containing at most 2 vertices.

    We will show that $G$ cannot contain as induced subgraphs both
    one of the graphs in Figure~\ref{fig:boundproof}.  These graphs are complements
    of each other, and we refer to them as $H$ and $H'$ respectively.

\begin{figure}[htb]
    \centering

@@

    Let $G_1$ be an induced
    subgraph of $G$ that is isomorphic to $H$.  Since there are
    no edges between the two three-vertex cliques in $G_1$, it must be the case that the
    vertex set of at least one of these cliques does not intersect $S_1$.
    Since $S_2$ is an independent set in $G$, this clique must have exactly
    one vertex in $S_2$ and two vertices in $S_3$.  We can deduce, then, that
    $S_3$ contains exactly two vertices, and that these vertices are adjacent in $G$.

    Now consider graph $H'$.  Since $H'$ is an induced subgraph of $G$, it
    follows by taking complements of $H'$ and $G$ that $H$ is an induced
    subgraph of $G'$ (the complement of $G$).  We can repeat the argument
    of the previous paragraph with the roles of $S_1$ and $S_2$ reversed to
    show that the two vertices in $S_3$ must be adjacent in the complement of
    $G$, and therefore must not be adjacent in $G$.  Since we previously showed that
    these vertices are adjacent in $G$, we have a contradiction.
\end{proof}

To give an upper bound of 14 on $f(6)$, Figure~\ref{fig:adjmat14} shows the
adjacency matrix of a 14-vertex graph that is induced universal for the family
of all graphs on six vertices.  This was generated using a simple local search
algorithm.  We begin by generating a random graph on 14 vertices as follows.
We number the vertices from zero; the generator makes the
$k$ vertices numbered $0$ to $k-1$ a clique, and the $k$ vertices numbered $k-1$ to $2k-2$ an
independent set.  Each possible edge that is not involved in either the clique
or the independent set is added with probability $1/2$.
We then repeatedly ``flip'' the status of a random edge from present to absent
or vice versa, but always leave the large clique and independent set intact.
After each flip, we count the number of 156 graphs on 6 vertices that are isomorphic
to a subgraph of our 14-vertex graph.  If the most recent flip resulted in a decrease
in this number, we revert it.  After each 1000 flips, we restart the algorithm
with a new random graph.

\begin{figure}[htb]
\centering
\small
\verb|0 1 1 1 1 1 0 1 1 0 0 0 1 0| \\
\verb|1 0 1 1 1 1 1 1 1 1 1 0 0 1| \\
\verb|1 1 0 1 1 1 0 1 1 0 1 0 1 0| \\
\verb|1 1 1 0 1 1 1 0 0 0 1 1 0 0| \\
\verb|1 1 1 1 0 1 0 1 0 0 0 0 0 0| \\
\verb|1 1 1 1 1 0 0 0 0 0 0 1 0 1| \\
\verb|0 1 0 1 0 0 0 0 0 0 0 1 1 1| \\
\verb|1 1 1 0 1 0 0 0 0 0 0 1 1 0| \\
\verb|1 1 1 0 0 0 0 0 0 0 0 0 1 0| \\
\verb|0 1 0 0 0 0 0 0 0 0 0 1 0 1| \\
\verb|0 1 1 1 0 0 0 0 0 0 0 1 1 0| \\
\verb|0 0 0 1 0 1 1 1 0 1 1 0 0 1| \\
\verb|1 0 1 0 0 0 1 1 1 0 1 0 0 0| \\
\verb|0 1 0 0 0 1 1 0 0 1 0 1 0 0|
\caption{The adjacency matrix of a 14-vertex induced universal graph for the family of all
six-vertex graphs}
\label{fig:adjmat14}
\end{figure}

\section{Bounds on $f(7)$}

By Proposition~\ref{f6proposition}, we have $f(7) \geq 16$.  Figure~\ref{fig:adjmat18}
shows the adjacency matrix of an 18-vertex induced universal
graph for the family of all seven-vertex graphs. This was generated with 
the heuristic described in Section~\ref{sec:f6}, with 10000 rather than 1000
edge-flips permitted before each restart.

Thus we have $16 \leq f(7) \leq 18$.

\begin{figure}[htb]
\centering
\small
\verb|0 1 1 1 1 1 1 1 1 1 0 1 1 1 1 1 0 0| \\
\verb|1 0 1 1 1 1 1 0 1 1 1 0 1 1 0 1 0 0| \\
\verb|1 1 0 1 1 1 1 1 0 1 0 1 0 0 0 0 0 1| \\
\verb|1 1 1 0 1 1 1 0 1 0 0 1 0 0 0 0 0 1| \\
\verb|1 1 1 1 0 1 1 1 1 0 0 0 0 0 1 0 0 0| \\
\verb|1 1 1 1 1 0 1 0 1 0 0 0 0 1 1 1 1 1| \\
\verb|1 1 1 1 1 1 0 0 0 0 0 0 0 1 0 0 0 1| \\
\verb|1 0 1 0 1 0 0 0 0 0 0 0 0 0 1 1 1 0| \\
\verb|1 1 0 1 1 1 0 0 0 0 0 0 0 1 1 1 0 1| \\
\verb|1 1 1 0 0 0 0 0 0 0 0 0 0 0 1 1 1 1| \\
\verb|0 1 0 0 0 0 0 0 0 0 0 0 0 1 0 0 1 0| \\
\verb|1 0 1 1 0 0 0 0 0 0 0 0 0 0 1 1 1 0| \\
\verb|1 1 0 0 0 0 0 0 0 0 0 0 0 0 0 1 1 1| \\
\verb|1 1 0 0 0 1 1 0 1 0 1 0 0 0 0 0 0 1| \\
\verb|1 0 0 0 1 1 0 1 1 1 0 1 0 0 0 0 0 1| \\
\verb|1 1 0 0 0 1 0 1 1 1 0 1 1 0 0 0 1 1| \\
\verb|0 0 0 0 0 1 0 1 0 1 1 1 1 0 0 1 0 1| \\
\verb|0 0 1 1 0 1 1 0 1 1 0 0 1 1 1 1 1 0|
\caption{The adjacency matrix of an 18-vertex induced universal graph for the family of all
seven-vertex graphs}
\label{fig:adjmat18}
\end{figure}

\section{Trees}\label{sec:trees}

@@

\begin{figure}[htb]
    \centering
\begin{tikzpicture}[>=latex',line join=bevel,scale=.4]
  \pgfsetlinewidth{.5bp}
%%
\pgfsetcolor{black}
  % Edge: 6 -- 0
  \draw [] (33.468bp,122.33bp) .. controls (44.467bp,128.89bp) and (59.197bp,137.66bp)  .. (70.288bp,144.27bp);
  % Edge: 6 -- 1
  \draw [] (30.834bp,100.1bp) .. controls (39.774bp,91.035bp) and (51.646bp,78.993bp)  .. (60.571bp,69.941bp);
  % Edge: 7 -- 0
  \draw [] (108.35bp,211.0bp) .. controls (103.69bp,198.96bp) and (97.434bp,182.81bp)  .. (92.754bp,170.73bp);
  % Edge: 7 -- 2
  \draw [] (128.78bp,216.26bp) .. controls (138.81bp,207.93bp) and (152.29bp,196.74bp)  .. (162.31bp,188.42bp);
  % Edge: 7 -- 3
  \draw [] (111.85bp,245.92bp) .. controls (109.9bp,257.68bp) and (107.35bp,272.94bp)  .. (105.4bp,284.67bp);
  % Edge: 8 -- 0
  \draw [] (134.88bp,109.4bp) .. controls (124.44bp,118.9bp) and (110.07bp,131.98bp)  .. (99.64bp,141.47bp);
  % Edge: 8 -- 1
  \draw [] (132.46bp,88.608bp) .. controls (119.73bp,81.799bp) and (101.96bp,72.297bp)  .. (89.227bp,65.491bp);
  % Edge: 8 -- 2
  \draw [] (154.41bp,114.43bp) .. controls (159.1bp,127.91bp) and (165.58bp,146.51bp)  .. (170.24bp,159.91bp);
  % Edge: 8 -- 4
  \draw [] (166.38bp,93.965bp) .. controls (179.82bp,91.611bp) and (198.11bp,88.409bp)  .. (211.53bp,86.058bp);
  % Edge: 8 -- 5
  \draw [] (152.57bp,79.558bp) .. controls (155.7bp,66.447bp) and (159.96bp,48.609bp)  .. (163.09bp,35.509bp);
  % Node: 0
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (86.17bp,153.73bp) ellipse (18.0bp and 18.0bp);
\end{scope}
  % Node: 1
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (73.34bp,56.99bp) ellipse (18.0bp and 18.0bp);
\end{scope}
  % Node: 2
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (176.16bp,176.91bp) ellipse (18.0bp and 18.0bp);
\end{scope}
  % Node: 3
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (102.42bp,302.6bp) ellipse (18.0bp and 18.0bp);
\end{scope}
  % Node: 4
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (229.48bp,82.92bp) ellipse (18.0bp and 18.0bp);
\end{scope}
  % Node: 5
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (167.27bp,18.0bp) ellipse (18.0bp and 18.0bp);
\end{scope}
  % Node: 6
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (18.0bp,113.12bp) ellipse (18.0bp and 18.0bp);
\end{scope}
  % Node: 7
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (114.87bp,227.81bp) ellipse (18.0bp and 18.0bp);
\end{scope}
  % Node: 8
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (148.38bp,97.12bp) ellipse (18.0bp and 18.0bp);
\end{scope}
%
\end{tikzpicture}
